The `rvertnet` package interacts with the API services of [VertNet](http://vertnet.org/index.php). No API key is needed. 

This tutorial will go through three use cases to demonstrate the kinds of things possible in `rvertnet`.

+ 
+ 
+ 
+ 
+ 

***
### Load package from GitHub
```{r loadpacakge}
# install_github("rvertnet", "ropensci")
library(rvertnet)
```

***

#### Get genotype data for all users at a particular snp.
```{r allgensnp}

```

***

#### Get genotype data for one or multiple users.
```{r genotypes}

```

***

### Get phenotype data for one or multiple users.
```{r phenotypes}

```


***

### Get openSNP user information.
```{r users}

```


***

### Download genotype data for a user from 23andme or other repo.
```{r fetch_genotypes}

```


***

### Get all known variations and all users sharing that phenotype for one phenotype(-ID).
```{r phenotypes_byid}

```


***

### Get all SNPedia/PLos/Mendeley-annotations for a specific SNP.
```{r annotations}

```


***

### Get all phenotypes, their variations, and how many users have data available for a given phenotype.
```{r allphenotypes}

```