The `rvertnet` package interacts with the API services of [VertNet](http://vertnet.org/index.php). No API key is needed. 

This tutorial will go through three use cases to demonstrate the kinds of things possible in `rvertnet`.

+ 
+ 
+ 
+ 
+ 

***
### Load package from GitHub
```{r loadpacakge}
# install_github("rvertnet", "ropensci")
library(rvertnet)
```

***

#### Get Darwin Core terms.
```{r loaddata}
data(dcnames)
head(dcnames)

data(dc)
head(dc)
```

***

#### Get metadata about maps currently available for querying against.
```{r vertavailablemaps}
head( vertavailablemaps()[,-4] )
```

***

### Get locations and number of occurrence records for an organism.
```{r vertlocations}
out <- vertlocations(t="notropis", d=2009)
head( out[,c(1,2,5,6,7)] )
```


***

### Get occurrence records.
```{r vertoccurrence}
# A simple example
vertoccurrence(t="notropis",num=5)[,1:5]

# More complicatd example visualizing results
library(rvertnet)
bluej1=vertoccurrence(t="Cyanocitta cristata",grp="bird")
bluej2=subset(bluej1,Latitude !=0 & Longitude != 0)
scrubj1=vertoccurrence(t="Aphelocoma",grp="bird")
scrubj2=subset(scrubj1,Latitude !=0 & Longitude != 0)

library(maps)
library(ggplot2)
world = map_data("world")
ggplot(world, aes(long, lat)) +
  geom_polygon(aes(group = group), fill = "white", color = "gray40",
               size = .2) +
  geom_jitter(data = bluej2,
              aes(Longitude, Latitude), alpha=0.6, size = 1,
              color = "blue") +
                opts(title = "Blue Jay and Scrub Jay") +
  geom_jitter(data = scrubj2,
              aes(Longitude, Latitude), alpha=0.6, size = 1,
              color = "brown")
```


***

### Get number of occurrence records.
```{r vertoccurrencecount}
vertoccurrencecount(t="notropis", d=2009)
```


***

### Get data providers for an organism.
```{r }
head( vertproviders(t="notropis")[,-1] ) # not showing institution name for brevity
```


***

### Search for occurrences for a given taxonomic name.
```{r }
head( vertsearch("aves", "california", 10)[,c(11,14)] ) # just lat/long for brevity
```