<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{rvertnet introduction}
-->

rvertnet introduction
======

`rvertnet` is a client for interacting with [VertNet.org](http://vertnet.org/).

## Installation

You can install the stable version from CRAN:

```{r eval=FALSE}
install.packages("rvertnet")
```

Or the development version from GitHub using the `devtools` package:

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("ropensci/rvertnet")
```

```{r}
library('rvertnet')
```

## Search by term

Search for _Aves_ in the state of _California_, limit to 10 records

```{r}
res <- searchbyterm(class = "Aves", state = "California", limit = 10, verbose = FALSE)
head(res[,1:5])
```

Search for _Mustela nigripes_ in the states of _Wyoming_ or _South Dakota_, limit to 20 records

```{r}
res <- searchbyterm(specificepithet = "nigripes", genus = "Mustela", state = "(wyoming OR south dakota)", limit = 20, verbose=FALSE)
head(res[,1:4])
```

Search for class _Aves_, in the state of _Nevada_, with a coordinate uncertainty range (in meters) of less than 25 meters

```{r}
res <- searchbyterm(class = "Aves", stateprovince = "Nevada", error = "<25", verbose=FALSE)
head(res[,1:5])
```

## Email dump of data

Specifies a termwise search (like `searchbyterm()`), but requests that all available records be made available for download as a tab-delimited text file.

```{r eval=FALSE}
bigsearch(genus = "ochotona", rfile = "mydata", email = "you@gmail.com")
#> Processing request...
#> 
#> Download of records file 'mydata' requested for 'you@gmail.com'
#> 
#> Query/URL: "http://api.vertnet-portal.appspot.com/api/download?q=%7B%22q%22:%22genus:ochotona%22,%22n%22:%22mydata%22,%22e%22:%22you@gmail.com%22%7D"
#> 
#> Thank you! Download instructions will be sent by email.
```

## Spatial search

Spatial search service allows only to search on a point defined by latitude and longitude pair, with a radius (meters) from that point. All three parameters are required. 

```{r}
res <- spatialsearch(lat = 33.529, lon = -105.694, radius = 2000, limit = 10, verbose = FALSE)
head(res[,1:5])
```

## Messages

In the previous examples, we've suppressed messages for more concise output, but you can set `verbose=TRUE` to get helpful messages - `verbose=TRUE` is also the default setting so if you don't specify that parameter messages will be printed to the console. 

```{r}
res <- searchbyterm(class = "Aves", state = "California", limit = 10, verbose = TRUE)
```
